### 2021-03-28 final_report/include/CE.tex
added a couple of clarifications

\begin{criterion}[POS-equivalence] \label{poseq}
 Two dependency trees $t$, $u$ are POS-equivalent (and, as such, will be aligned) if $M_1 = M_2 \neq \emptyset$, where $M_i$ is defined as the multiset of POS tags of all the meaning-carrying word nodes of $t_i$. 
\end{criterion} \smallskip

>>>>

\begin{criterion}[POS-equivalence] \label{poseq}
 Two dependency trees $t$, $u$ are POS-equivalent (and, as such, will be aligned) if $M_1 = M_2 \neq \emptyset$, where $M_i$ is defined as the multiset of POS tags of all the \normalfont{meaning-carrying} \textit{(see below) word nodes of $t_i$}. 
\end{criterion} \smallskip
